Extracting data from vector figures in scholarly articles

### 2018-03-12 submission/manuscript.Rmd
Update PMR affiliation

---
title: "Extracting data from vector figures in scholarly articles"
author: CHJ Hartgerink (Tilburg University, c.h.j.hartgerink@uvt.nl), Peter Murray-Rust
  (Cambridge University, pm286@cam.ac.uk)
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    fig_caption: yes
    toc: no
    toc_depth: 2
  includes:
    in_header: hypothesis.html
  pdf_document: default
  word_document: default
bibliography: ../library.bib
link-citations: true
---

>>>>

---
title: "Extracting data from vector figures in scholarly articles"
author: CHJ Hartgerink (Tilburg University, c.h.j.hartgerink@uvt.nl), Peter Murray-Rust
  (ContentMine, info@contentmine.org)
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    fig_caption: yes
    toc: no
    toc_depth: 2
  includes:
    in_header: hypothesis.html
  pdf_document: default
  word_document: default
bibliography: ../library.bib
link-citations: true
---
